A Meta-analysis of Longevity Estimates of Mosquito Vectors of Disease: Figures

### 2020-11-21 writeUp/figures.tex
updated graph titles

\begin{figure}[h]
	\centerline{\includegraphics[width=1.3\textwidth]{./Figure_files/mrr_elpd_vs_exponential_ordered.pdf}}
	\caption{\textbf{Detecting senescence in MRR studies.} Here, we consider the predictive accuracy of age-dependent models of mortality versus the exponential model by species. The predictive accuracy was determined using K-Fold cross-validation as described in SOM; the measure of accuracy presented here by the central dots is the difference in estimated expected log pointwise predictive density compared to the exponential model. The lower and upper whiskers represent the lower and upper bounds of the 95\% confidence interval in predictive accuracy. The species have been ordered so that those with the highest average predictive accuracy across all age-dependent models compared to the exponential model appear at the top. If all age-dependent models outperform the exponential, we deem this as evidence for age-dependent mortality (`+'); if a subsample of models perform better, we deem the evidence ambiguous (`?'); and if no age-dependent model exceeds the performance of the exponential, we conclude no evidence in favour of senescence (`-').}
	\label{fig:mrr_elpd}
\end{figure}

>>>>

\begin{figure}[h]
	\centerline{\includegraphics[width=1.3\textwidth]{./Figure_files/mrr_elpd_vs_exponential_ordered.pdf}}
	\caption{\textbf{Evidence for senescence: MRR studies.} Here, we consider the predictive accuracy of age-dependent models of mortality versus the exponential model by species. The predictive accuracy was determined using K-Fold cross-validation as described in SOM; the measure of accuracy presented here by the central dots is the difference in estimated expected log pointwise predictive density compared to the exponential model. The lower and upper whiskers represent the lower and upper bounds of the 95\% confidence interval in predictive accuracy. The species have been ordered so that those with the highest average predictive accuracy across all age-dependent models compared to the exponential model appear at the top. If all age-dependent models outperform the exponential, we deem this as evidence for age-dependent mortality (`+'); if a subsample of models perform better, we deem the evidence ambiguous (`?'); and if no age-dependent model exceeds the performance of the exponential, we conclude no evidence in favour of senescence (`-').}
	\label{fig:mrr_elpd}
\end{figure}
